%! Author = kid-a
%! Date = 9/30/25

% Preamble
\documentclass[11pt]{book}

% Packages
\usepackage{amsmath}
\usepackage[top=2cm,bottom=2cm,left=2cm, right=2cm]{geometry}
\usepackage{hyperref}
\usepackage{fancyhdr}

\title{Grand Plan}
\author{Independent Society of Knowledge}
\date{last update \today}

% Document
\begin{document}
    \maketitle
    \tableofcontents
    \newpage


    \chapter{About This Document}\label{ch:about-this-document}
    \input{content/about-this-document}


    \chapter{Introduction}\label{ch:introduction}
    \input{content/introduction}


    \chapter{Critique}\label{ch:critique}
    \input{critique}

    \chapter{Decentralization}\label{ch:decentralization}
    This section requires extension.
    \chapter{Open Collaboration}\label{ch:open-collaboration}
    This section requires extension.
    \chapter{Free-Market for Knowledge}\label{ch:free-market-for-knowledge}
    This section requires extension.

    \chapter{Ecosystem}\label{ch:ecosystem}
    Independent Society of Knowledge (ISK) aims to solve the solutions mentioned in \autoref{ch:introduction} and \autoref{ch:critique} by providing a comprehensive ecosystem of goods and services that facilitate open collaboration, decentralization, and a free-market for knowledge.

    The ISK ecosystem, consists of platforms, software tools, initiative, and services that would allow the scientific community to thrive in an open, collaborative, and decentralized environment, while keeping the core values of rigorous scientific methods, and high-quality standards.

    In this chapter, we would briefly cover the main components of the ecosystem, how they connect to one another, and how they contribute to the overall vision of ISK\@.

    \section{Grand View}\label{sec:grand-view}
    To achieve such a vision, multiple services are needed, active and passive initiatives, and tools that would allow the community to gain momentum in the direction of decentralization, open-collaboration, and free-market.
    Our passive initiatives include:
    \begin{itemize}
        \item Advocacy for open-collaboration, decentralization, and free-market for knowledge.
        \item Education and awareness campaigns to inform the community about the benefits of our vision.
        \item Building partnerships with like-minded organizations and institutions to promote our vision.
        \item Licensing and Attribution methods that would allow researchers to retain their rights, while also allowing others to build upon their work.
    \end{itemize}
    Our active initiatives include:
    \begin{itemize}
        \item Koncept: An Integrated Research Environment (IRE) that provides a suite of tools for research at individual level.
        While also providing a new type of document within the academic system that is dynamic, and makes researches more open for collaboration, and branching.
        \item Open-Journal: A decentralized, open-access journal platform that allows researchers to publish their work without the need for traditional publishers.
        This also includes a social platform for researchers that facilitates collaboration, networking, and knowledge sharing.
        The platform would include Koncept integration, Open-Lectures, and other tools to embrace researching experience, as well as communication and collaboration.
        \item Community-Integration: Our projects need to be integrated with other solutions in the community as well.
        Projects like ArXiv, Zenodo, and others that provide open-access to research outputs.
    \end{itemize}

\end{document}
